Sampling-Based Motion Planning for Tracking Evolution of Dynamic Tunnels in Molecular Dynamics Simulations

### 2017-10-31 paper.tex
experiments small changes

\begin{figure}
\centering
{
\renewcommand{\tabcolsep}{1pt}
\begin{tabular}{cccccc}
\includegraphics[width=0.15\textwidth]{fig/merging1} &
\includegraphics[width=0.15\textwidth]{fig/merging2} &
\includegraphics[width=0.15\textwidth]{fig/merging3} &
\includegraphics[width=0.15\textwidth]{fig/merging4} &
\includegraphics[width=0.15\textwidth]{fig/merging5} &
\includegraphics[width=0.15\textwidth]{fig/merging6}  \\
a (frame $i$) & b (frame $i+1$) & c (frame $i+1$) & d (frame $i+2$)  & e (frame $i+2$) & f (frame $i+2)$ \\
detected      & tree transfer   & void space      & tree transfer    & void space      & merging   \\
void space    & (splitting)      & detection       &  (splitting)     &  detection      & \\              
\end{tabular}
\caption{\label{fig::merging}
An example of merging.
The tree in the first frame with a denoted motion of one of the atoms (a). 
A path exists between the nodes $A$ and $B$.
The moving atom in the second frame causes splitting of the detected void space to three components (b).
The components are expanded by new nodes (green) in the frame $i+1$ (c), but they are still too far so merging cannot connect them.
There is not any path between $A$ and $B$ in the frame $i+1$. 
In the third frame, atoms move back without colliding with any of the void space nodes (d).
The three components are further expanded (green nodes) in the third frame (e), but still there is not any path between $A$ and $B$.
The merging in the $i+2$ frame connects the tree components again (dotted lines) (f).
The result of the merging process is again the existing path between $A$ and $B$.
}
}
\end{figure}

@@

In each frame, the void space detection (Alg.~\ref{alg::main}) was performed with $\Imax=1200$ iterations.
The second phase of the search was switched after $\alpha=70$~\% of the iterations (i.e., after 840 iterations).
Other parameters and their values used for the computation were $m=8$, $\da=5$~\AA, $\db=0.5$~\AA, $\gb=0.1$, and $\dts=2$~\AA.

@@

The number of static tunnels decreases with the increasing probe size. 
In order to increase the number of frames with detected static tunnels, the biochemists usually analyze the tunnel with a smaller probe size, e.g., 1~\AA or even 0.9~\AA.
This leads to the detection of more tunnels, but on the other hand, their bottleneck may be too narrow for the passage of certain ligands.
In the described experiment, we analyzed the proteins with a very large probe size (1.4~\AA).

>>>>

\begin{figure}
\centering
{
\renewcommand{\tabcolsep}{1pt}
\begin{tabular}{cccccc}
\includegraphics[width=0.15\textwidth]{fig/merging1} &
\includegraphics[width=0.15\textwidth]{fig/merging2} &
\includegraphics[width=0.15\textwidth]{fig/merging3} &
\includegraphics[width=0.15\textwidth]{fig/merging4} &
\includegraphics[width=0.15\textwidth]{fig/merging5} &
\includegraphics[width=0.15\textwidth]{fig/merging6}  \\
a (frame $i$) & b (frame $i+1$) & c (frame $i+1$) & d (frame $i+2$)  & e (frame $i+2$) & f (frame $i+2)$ \\
detected      & tree transfer   & void space      & tree transfer    & void space      & merging   \\
void space    & (splitting)      & detection       &  (splitting)     &  detection      & \\              
\end{tabular}
\caption{\label{fig::merging}
An example of void space merging and splitting.
The tree in the first frame with a denoted motion of one of the atoms (a). 
A path exists between the nodes $A$ and $B$.
The moving atom in the second frame causes splitting of the detected void space to three components (b).
The components are expanded by new nodes (green) in the frame $i+1$ (c), but they are still too far so merging cannot connect them.
There is not any path between $A$ and $B$ in the frame $i+1$. 
In the third frame, atoms move back without colliding with any of the void space nodes (d).
The three components are further expanded (green nodes) in the third frame (e), but still there is not any path between $A$ and $B$.
The merging in the $i+2$ frame connects the tree components again (dotted lines) (f).
The result of the merging process is again the existing path between $A$ and $B$.
}
}
\end{figure}

@@

In each frame, the void space detection (Alg.~\ref{alg::main}) was performed with $\Imax=1,200$ iterations.
The second phase of the search was switched after $\alpha=70$~\% of the iterations (i.e., after 840 iterations).
Other parameters and their values used for the computation were $m=8$, $\da=5$~\AA, $\db=0.5$~\AA, $\gb=0.1$, and $\dts=2$~\AA.

@@

The number of static tunnels decreases with the increasing probe size. 
In order to increase the number of frames with detected static tunnels, the biochemists usually analyze the tunnel with a smaller probe size, e.g., 1~\AA\ or even 0.9~\AA.
This leads to the detection of more tunnels, but on the other hand, their bottleneck may be too narrow for the passage of certain ligands.
In the described experiment, we analyzed the proteins with a very large probe size (1.4~\AA).
